Improving reproducibility of scientific software using Nix/NixOS: A case study on the preCICE ecosystem

### 2024-05-10 paper/paper.tex
reformat(paper): Reformat sentence so it looks better

Most of the functionality that can be found in the official VM is also available in our NixOS VM and all preCICE tutorials could be run successfully, except \texttt{flow-over-heated-plate-steady-state} as the manual steps involved were unclear, \texttt{partitioned-heat-conduction-complex} and \texttt{partitioned-heat-conduction-direct} as the \texttt{mshr} python dependency was missing and \texttt{turek-hron-fsi3} as the tutorial needs \texttt{swak4foam}, an add-on to OpenFOAM, we were not able to package.

>>>>

\begin{sloppypar}
Most of the functionality that can be found in the official VM is also available in our NixOS VM and all preCICE tutorials could be run successfully, except \texttt{turek-hron-fsi2} as the tutorial needs \texttt{swak4foam}, an add-on to OpenFOAM, we were not able to package, \texttt{flow-over-heated-plate-steady-state} as the manual steps involved were unclear, \texttt{partitioned-heat-conduction-complex} and \texttt{partitioned-heat-conduction-direct} as the \texttt{mshr} python dependency was missing.
\end{sloppypar}
